Global Reach or Out of Reach

### 2019-05-15 Paper_markdown.Rmd
use parenthetical citations; fix figure labels

When Xerxes sought in invade the Greek peninsula, he used several hundred ships lined side by side with wooden planks running between creating a bridge to cross his armies over the Hellespont.  Despite using his own vessels to build this massive bridge, he still had nearly a thousand warships with which to threaten the Greek coast.  The war between Athens and Sparta decades later for domination of Greece began partly as a result of the buildup of Athenian naval power and threat of Athenian control over the Greek trade routes.  In the age of sail the most dominant colonial powers were those with the greatest navies allowing them to protect trade routes and spread their empire through overseas colonization.  In the Second World War the British and American navies protected the vital convoys which supplied the British and prevented the final bastion of European resistance from falling to the German war machine.  Naval power has been the backbone of every great empire from antiquity to modernity.  No major power can become a global power if they are not dominant in terms of naval capabilities. But can the powerful fleets of a world power affect the conflicts the occur between the lesser powers in the international system?  The various schools of international relations theory argue that a hegemon will punish actors who attempt to upset the status quo.  If a state believes that the hegemon will respond to aggression, does the ability of the hegemon to project power overseas influence the conflictual behavior and decision making of that state?  This paper will investigate this question and explore any relationships between a hegemon’s naval capability and the conflict behavior of other states in the international system. 
Using several models of logistic regression, this paper will analyze the relationship between militarized interstate dispute onset and severity and the naval capabilities of a hegemonic power. The following sections will consist of a review of the prevailing literature on hegemony and conflict initiation as well as the operationalization and effect of naval capabilities. I will introduce the theory and the data and methods used in this paper in further detail in the section following that literature review.  An analysis of the results and a discussion of the implications of this research will conclude the paper.

@@

The gravitational pull in this case is the power of the state.  The most powerful states in the international system can establish rules and order in the international system as they see fit and punish or reward adherence to that order.  The most powerful of these states is commonly refered to the hegemon.  The concept of power in international relations is at best vague and open to interpretation.  However, despite its ambiguity it has been the foundation of international relations research and theory.  A full examination of the lexicon of the literature which seeks to define power is beyond the scope of this paper. For my purposes I observe power in the same way as A.F.K. Organski, the ability of a state to change the behavior of another @Organski1968.  We can observe this ability by measuring the determinants of power; the resources and material capabilities which allow states to interact and influence each other.  In this research a specific aspect of the international power of states and the hegemon, naval capability, will be the focus.

The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership @Smith2012. According to several schools of international relations theory, the hegemon will establish order in the international system and will endeavor to keep the order. George Modelski (1978) referred to the hegemon as the world power and argued that these states were those entities which had a monopoly on “order-keeping” of the world system. It was the task of the world power to manage the interdependence of the other units in the international system.  What provided these world powers the ability to do so, according to Modelski, was their overwhelming advantage in naval capabilities.  States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities. Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide. @Calder2007.  All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power @Modelski1978.

However, there are theorists like John Mearsheimer who argue that naval power has little to do with the establishment or maintenance of a hegemonic order.  According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power @Mearsheimer2001.  He even goes as far as to argue that no state can achieve hegemony due to the great stopping power of the world oceans. Navies, in the eyes of Mearsheimer, are force multipliers for the land forces and should be considered as supporting the army, not as a potential independent tool for preventing or resolving conflict.

The explanatory variable in this research is the naval capabilities of the prevailing hegemon. A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land @Corbett1984 @Mahan2004 @Mearsheimer2001.  Naval forces have evolved over time with new technologies and changing tactics, but much of the strategy and purpose of naval forces have remained the same.  States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests. This includes preventing foreign powers from establishing what some refer to as “command of the sea” @Corbett1984. One of the seminal works on the importance of naval power comes from Alfred Mahan.  Mahan argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests @Mahan2004.  Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce. @Crowl1986.  The two most common ways in which to measure naval power is by looking at the number of capital ships a state maintains and by observing the total tonnage of all blue-water capable ships in the states inventory.  I will review each method in the next few sections.

Not all naval forces are alike.  States will design their naval forces based on the nature of the mission objectives as well as the area in which those forces will operate.  A state which uses its navy to protect its coastline and exclusive economic zone will use ships designed for green-water warfare, specializing in littoral operations in shallow waters and mine clearing.  States which seek to project power a great distance and engage the navies of other states will design their naval forces for blue-water operations and long-range missions. The backbone of any naval force is the warship, the vessel which engages in combat with opposing fleets or non-state actors such as pirates.  Capital ships are often the largest and most heavily armed warships of any fleet and are capable of traveling the greatest distance.  A single capital ship can destroy entire squadrons of smaller vessels and devastate a coastline.  During the Second World War, the German battleships Bismarck and Tirpitz were designed to single handedly attack entire allied shipping convoys.  In the Pacific theater the naval conflict centered around the battleship and carrier forces of the American and Imperial navies.  The primary targets of the Japanese forces during the attack on Pearl Harbor were the American carriers and battleships tied up in the harbor. George Modelski uses capitol ships in his study of naval power and long cycles in international politics @Modelski1987 Modelski1988.

Sean Bolks and Richard Stoll also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power @Bolks2000. They chose this measure over the far more common method of observing the state’s military spending because it offered several benefits.  First, it avoids some of the greatest problems associated with using military expenditure, differences in the definition and rates of military expenditures in different states. The authors use the examples of conscripts, volunteers, and retirees. Some states have militaries which rely heavily on conscription as opposed to volunteers. This allows them to pay significantly less for a military of the same size as a state which pays for volunteers. There is also issues with what exactly is considered part of military expenditures. Some countries include pensions for retirees and healthcare for their veterans as military expenditures, causing a balloon in their spending while not contributing to their forces size or capability. Other countries have even provided massive subsidies to their domestic military industries resulting in additional massive hikes in their annual military spending without any contribution to force size or composition. Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state @Bolks2000.

An obvious question that arises here is what constitutes a capital ship.  During what is commonly referred to as the age of sail, a capital ship would have been a ship of the line.  These large sail powered vessels were armed with multiple rows of cannon which could deliver powerful broadsides.  A large ship of the line such as the Spanish Santisima Trinidad carried more than 140 cannons; as many as entire land armies.  The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries @Keegan1993.  However, during the interwar period states began experimenting with new technologies which gave rise to new classes of warships.  The aircraft carrier allowed a fleet to project offensive force hundreds of miles beyond the rand of the big gun battleships, and submarines allowed for stealthy operations below the surface. By the end of the war the powerful battlewagons which had ruled the waves for decades had been rendered obsolete.  Today the criteria for a capital ship is as ambiguous as ever.  No battleships remain in service anywhere in the world.  Carriers and nuclear submarines are seen as the hallmarks of an advanced navy and some classes of destroyers today weigh as much as World War 1 battleships.  Bolks and Stoll use the number of capital ships recorded in the data compiled by Modelski in their study of global naval power @Bolks2000. Modelski and Thompson observed that what constitutes a capital ship changes over the years, as described above. Thus, they change their operationalization of a capital ship in their own dataset to account for the changes in technology and definition.

Aside from the type of ship, one of the most common ways to measure the capabilities of a fleet is by looking at the total tonnage of every ship in a states inventory.  Larger ocean-going vessels and the modern equivalent of the capital ships are incredibly heavy machines.  A larger vessel is able to carry more weapons, armor, and aircraft than a smaller ship making it a more dangerous weapon.  It was for this reason that states have sought to limit the size of warships in the past.  The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage @Gray2007 @McBride1997.  Joseph Maiolo examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries @Maiolo2008. William Walters examined the history of American naval shipbuilding and capability in his historical review of U.S. naval ship building @Walters2000. Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities. @Wolters2011

The number of capital ships and the total tonnage of naval inventory are the two most common methods of measuring naval capability.  However, these measures do not capture one vital concept of capability, the technological quality and efficiency of a navy.  At the battle of Lepanto (1571) the combined European powers making up the Holy League faced the fleet of the Ottoman Empire.  Both fleets contained roughly the same number of ships and the same type, roughly 200 galleys using oars and sails.  The Europeans however also had six new galleasses which were the precursors to the large mast ships of the age-of-sail and were heavily armed for their time.  These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition @Keegan1993.  More recent examples of the importance of technological capability were the submarine races of the Cold War.  Both the Soviet Union and the United States sought to make their submarines stealthier and more destructive by making them nuclear powered and giving them the ability to launch missiles from underwater.  China today has more submarines in their fleet than the United States. However, most of these ships are older diesel-powered models with a limited range.  The advanced nuclear-powered submarines used by the United States are quitter, faster, and far more advanced. This shortcoming of tonnage and ship counts as measures of naval power was recognized at the Washington Naval Conference by the United States which felt it was getting cheated.  Woodrow Wilson ordered an engineer to develop what he called a technical yardstick to identify the qualitative differences between ships. However, this yardstick was rejected by the other members of the conference and the terms of the treaty called for reductions in tonnage.  A key question in this research is how to incorporate a measure of technological advancement into the measure of naval capability McBride1997.

## Theory
	In this paper I make several assumptions about the international system as well as the actors who occupy it. First, unlike John Mearsheimer I assume that states are able to become a global hegemon, and they are able to do so thanks to an overwhelming advantage in naval capabilities. Naval power allows a state to control the international shipping lanes, land troops on foreign shores, and protect supply routes from across the sea thus allowing invasion forces to remain supplied and reinforced. Without a powerful navy, no state can become a hegemon, but this does not mean that a state cannot gain the naval capabilities necessary to create and enforce and international order.
	Other states in the international system will understand that the hegemon has an interest in maintaining the status quo and that the hegemon will punish those who try to upset the international order. With this in mind, states will be less inclined to engage in conflictual behavior and risk the hegemon responding. Unless that state shares a land border with the hegemon, thill will mean that the state will be wary of the hegemon’s naval capabilities as it will be their navy that allows them to respond to any action in the international system. In this paper I present two simple hypotheses:
H1) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID in a given year.
H2) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID which involves the use of force in a given year.
I expect the results of my statistical test to show a statistically significant negative relationship between the hegemon’s naval capabilities and the likelihood of a MID occurring. Additionally, I expect that each of the additional controls I am including will be statistically significant, as each of them have been found to be so in different studies.

@@

```{r tonnage_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Tonnage per year"}
plot(Master4$year, Master4$US_Tonnage, main="US Tonnage Over time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
```

@@

```{r Spending_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Spending per capita"}
plot(Master4$year, Master4$Spending_Per_Soldier, main="Spending per soldier",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
```

@@

```{r Naval_Capabilities_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Bivariate_Naval_Cap"}
plot(Master4$year, Master4$US_Naval_Cap, main="US Naval Capabilities Over Time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
    ```

>>>>

When Xerxes sought to invade the Greek peninsula, he used several hundred ships lined side by side with wooden planks running between creating a bridge to cross his armies over the Hellespont.  Despite using his own vessels to build this massive bridge, he still had nearly a thousand warships with which to threaten the Greek coast.  The war between Athens and Sparta decades later for domination of Greece began partly as a result of the buildup of Athenian naval power and threat of Athenian control over the Greek trade routes.  In the age of sail the most dominant colonial powers were those with the greatest navies allowing them to protect trade routes and spread their empire through overseas colonization.  In the Second World War the British and American navies protected the vital convoys which supplied the British and prevented the final bastion of European resistance from falling to the German war machine.  Naval power has been the backbone of every great empire from antiquity to modernity.  No major power can become a global power if they are not dominant in terms of naval capabilities. But can the powerful fleets of a world power affect the conflicts the occur between the lesser powers in the international system?  The various schools of international relations theory argue that a hegemon will punish actors who attempt to upset the status quo.  If a state believes that the hegemon will respond to aggression, does the ability of the hegemon to project power overseas influence the conflictual behavior and decision making of that state?  This paper will investigate this question and explore any relationships between a hegemon’s naval capability and the conflict behavior of other states in the international system. 
Using several models of logistic regression, this paper will analyze the relationship between militarized interstate dispute onset and severity and the naval capabilities of a hegemonic power. The following sections will consist of a review of the prevailing literature on hegemony and conflict initiation as well as the operationalization and effect of naval capabilities. I will introduce the theory and the data and methods used in this paper in further detail in the section following that literature review.  An analysis of the results and a discussion of the implications of this research will conclude the paper.

@@

The gravitational pull in this case is the power of the state.  The most powerful states in the international system can establish rules and order in the international system as they see fit and punish or reward adherence to that order.  The most powerful of these states is commonly refered to the hegemon.  The concept of power in international relations is at best vague and open to interpretation.  However, despite its ambiguity it has been the foundation of international relations research and theory.  A full examination of the lexicon of the literature which seeks to define power is beyond the scope of this paper. For my purposes I observe power in the same way as A.F.K. Organski, the ability of a state to change the behavior of another [@Organski1968].  We can observe this ability by measuring the determinants of power; the resources and material capabilities which allow states to interact and influence each other.  In this research a specific aspect of the international power of states and the hegemon, naval capability, will be the focus.

The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership [@Smith2012]. According to several schools of international relations theory, the hegemon will establish order in the international system and will endeavor to keep the order. George Modelski (1978) referred to the hegemon as the world power and argued that these states were those entities which had a monopoly on “order-keeping” of the world system. It was the task of the world power to manage the interdependence of the other units in the international system.  What provided these world powers the ability to do so, according to Modelski, was their overwhelming advantage in naval capabilities.  States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities. Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide [@Calder2007].  All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power [@Modelski1978].

However, there are theorists like John Mearsheimer who argue that naval power has little to do with the establishment or maintenance of a hegemonic order.  According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power [@Mearsheimer2001].  He even goes as far as to argue that no state can achieve hegemony due to the great stopping power of the world oceans. Navies, in the eyes of Mearsheimer, are force multipliers for the land forces and should be considered as supporting the army, not as a potential independent tool for preventing or resolving conflict.

The explanatory variable in this research is the naval capabilities of the prevailing hegemon. A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land [@Corbett1984; @Mahan2004; @Mearsheimer2001].  Naval forces have evolved over time with new technologies and changing tactics, but much of the strategy and purpose of naval forces have remained the same.  States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests. This includes preventing foreign powers from establishing what some refer to as “command of the sea” [@Corbett1984]. One of the seminal works on the importance of naval power comes from Alfred Mahan.  Mahan argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests [@Mahan2004].  Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce. [@Crowl1986].  The two most common ways in which to measure naval power is by looking at the number of capital ships a state maintains and by observing the total tonnage of all blue-water capable ships in the states inventory.  I will review each method in the next few sections.

Not all naval forces are alike.  States will design their naval forces based on the nature of the mission objectives as well as the area in which those forces will operate.  A state which uses its navy to protect its coastline and exclusive economic zone will use ships designed for green-water warfare, specializing in littoral operations in shallow waters and mine clearing.  States which seek to project power a great distance and engage the navies of other states will design their naval forces for blue-water operations and long-range missions. The backbone of any naval force is the warship, the vessel which engages in combat with opposing fleets or non-state actors such as pirates.  Capital ships are often the largest and most heavily armed warships of any fleet and are capable of traveling the greatest distance.  A single capital ship can destroy entire squadrons of smaller vessels and devastate a coastline.  During the Second World War, the German battleships Bismarck and Tirpitz were designed to single handedly attack entire allied shipping convoys.  In the Pacific theater the naval conflict centered around the battleship and carrier forces of the American and Imperial navies.  The primary targets of the Japanese forces during the attack on Pearl Harbor were the American carriers and battleships tied up in the harbor. George Modelski uses capitol ships in his study of naval power and long cycles in international politics [@Modelski1987; @Modelski1988].

Sean Bolks and Richard Stoll also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power [@Bolks2000]. They chose this measure over the far more common method of observing the state’s military spending because it offered several benefits.  First, it avoids some of the greatest problems associated with using military expenditure, differences in the definition and rates of military expenditures in different states. The authors use the examples of conscripts, volunteers, and retirees. Some states have militaries which rely heavily on conscription as opposed to volunteers. This allows them to pay significantly less for a military of the same size as a state which pays for volunteers. There is also issues with what exactly is considered part of military expenditures. Some countries include pensions for retirees and healthcare for their veterans as military expenditures, causing a balloon in their spending while not contributing to their forces size or capability. Other countries have even provided massive subsidies to their domestic military industries resulting in additional massive hikes in their annual military spending without any contribution to force size or composition. Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state [@Bolks2000].

An obvious question that arises here is what constitutes a capital ship.  During what is commonly referred to as the age of sail, a capital ship would have been a ship of the line.  These large sail powered vessels were armed with multiple rows of cannon which could deliver powerful broadsides.  A large ship of the line such as the Spanish Santisima Trinidad carried more than 140 cannons; as many as entire land armies.  The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries [@Keegan1993].  However, during the interwar period states began experimenting with new technologies which gave rise to new classes of warships.  The aircraft carrier allowed a fleet to project offensive force hundreds of miles beyond the rand of the big gun battleships, and submarines allowed for stealthy operations below the surface. By the end of the war the powerful battlewagons which had ruled the waves for decades had been rendered obsolete.  Today the criteria for a capital ship is as ambiguous as ever.  No battleships remain in service anywhere in the world.  Carriers and nuclear submarines are seen as the hallmarks of an advanced navy and some classes of destroyers today weigh as much as World War 1 battleships.  Bolks and Stoll use the number of capital ships recorded in the data compiled by Modelski in their study of global naval power [@Bolks2000]. Modelski and Thompson observed that what constitutes a capital ship changes over the years, as described above. Thus, they change their operationalization of a capital ship in their own dataset to account for the changes in technology and definition.

Aside from the type of ship, one of the most common ways to measure the capabilities of a fleet is by looking at the total tonnage of every ship in a states inventory.  Larger ocean-going vessels and the modern equivalent of the capital ships are incredibly heavy machines.  A larger vessel is able to carry more weapons, armor, and aircraft than a smaller ship making it a more dangerous weapon.  It was for this reason that states have sought to limit the size of warships in the past.  The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage [@Gray2007; @McBride1997].  Joseph Maiolo examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries [@Maiolo2008]. William Walters examined the history of American naval shipbuilding and capability in his historical review of U.S. naval ship building [@Walters2000]. Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities [@Wolters2011].

The number of capital ships and the total tonnage of naval inventory are the two most common methods of measuring naval capability.  However, these measures do not capture one vital concept of capability, the technological quality and efficiency of a navy.  At the battle of Lepanto (1571) the combined European powers making up the Holy League faced the fleet of the Ottoman Empire.  Both fleets contained roughly the same number of ships and the same type, roughly 200 galleys using oars and sails.  The Europeans however also had six new galleasses which were the precursors to the large mast ships of the age-of-sail and were heavily armed for their time.  These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition [@Keegan1993].  More recent examples of the importance of technological capability were the submarine races of the Cold War.  Both the Soviet Union and the United States sought to make their submarines stealthier and more destructive by making them nuclear powered and giving them the ability to launch missiles from underwater.  China today has more submarines in their fleet than the United States. However, most of these ships are older diesel-powered models with a limited range.  The advanced nuclear-powered submarines used by the United States are quitter, faster, and far more advanced. This shortcoming of tonnage and ship counts as measures of naval power was recognized at the Washington Naval Conference by the United States which felt it was getting cheated.  Woodrow Wilson ordered an engineer to develop what he called a technical yardstick to identify the qualitative differences between ships. However, this yardstick was rejected by the other members of the conference and the terms of the treaty called for reductions in tonnage.  A key question in this research is how to incorporate a measure of technological advancement into the measure of naval capability McBride1997.

## Theory
In this paper I make several assumptions about the international system as well as the actors who occupy it. First, unlike John Mearsheimer I assume that states are able to become a global hegemon, and they are able to do so thanks to an overwhelming advantage in naval capabilities. Naval power allows a state to control the international shipping lanes, land troops on foreign shores, and protect supply routes from across the sea thus allowing invasion forces to remain supplied and reinforced. Without a powerful navy, no state can become a hegemon, but this does not mean that a state cannot gain the naval capabilities necessary to create and enforce and international order.

Other states in the international system will understand that the hegemon has an interest in maintaining the status quo and that the hegemon will punish those who try to upset the international order. With this in mind, states will be less inclined to engage in conflictual behavior and risk the hegemon responding. Unless that state shares a land border with the hegemon, thill will mean that the state will be wary of the hegemon’s naval capabilities as it will be their navy that allows them to respond to any action in the international system. In this paper I present two simple hypotheses:

H1) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID in a given year.

H2) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID which involves the use of force in a given year.

I expect the results of my statistical test to show a statistically significant negative relationship between the hegemon’s naval capabilities and the likelihood of a MID occurring. Additionally, I expect that each of the additional controls I am including will be statistically significant, as each of them have been found to be so in different studies.

@@

```{r tonnage_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:tonnage}Tonnage per year"}
plot(Master4$year, Master4$US_Tonnage, main="US Tonnage Over time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
```

@@

```{r Spending_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:spending}Spending per capita"}
plot(Master4$year, Master4$Spending_Per_Soldier, main="Spending per soldier",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
```

@@

```{r Naval_Capabilities_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:capability}Bivariate Naval Capabilities"}
plot(Master4$year, Master4$US_Naval_Cap, main="US Naval Capabilities Over Time",
    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
    ```
